Demanding resources: Converging characteristics of challenge and resource

### 2022-10-28 copy of SIOP2023convergence.Rmd
note on "extent to which characteristic is present" variables being used as a moderator

>>>>

## Maybe do third moderator

We also have ratings of "...the extent to which this characteristic is present in your job". Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*. This is probably a better/more appropriate moderator than either of the above two...

### 2022-10-28 copy-of-SIOP2023convergence.tex
note on "extent to which characteristic is present" variables being used as a moderator

>>>>

\hypertarget{maybe-do-third-moderator}{%
\subsection{Maybe do third moderator}\label{maybe-do-third-moderator}}

We also have ratings of ``\ldots the extent to which this characteristic is present in your job''. Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}. This is probably a better/more appropriate moderator than either of the above two\ldots{}
